A studyforrest extension, an annotation of words and phonemes in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-04-15 paper/main.tex
Sort result figure and tables into text
Have a TODO list
Add TODOs for pieces that I thought we had agreed to remove

\begin{figure*}
  \centering
% \includegraphics[width=0.4\textwidth]{frog.jpg}
  \includegraphics[width=\linewidth]{figures/slicescolorbars}
  \caption{Mixed-effects group-level (N=14) GLM contrasts for the audio-description of the movie Forrest Gump. All cluster (Z>3.4, p<0.05; cluster corr.; MNI template space).}
  \label{fig:results}
\end{figure*}

\begin{table*}[t]
    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for the contrast words > no-speech.}
\label{tab:cope1}
\begin{tabular}{rrrrrrrrrrp{3cm}}
\toprule
& & & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{5-7} \cmidrule{8-10}
Cl.\-Index & Voxels & $p_{corr.}$ & Z\-max & X & Y & Z  & X & Y & Z & structure \\
\midrule
4 & 14990 & 0 & 6.31 & -49 & -24.7 & 6.35 & -54.8 & -32.5 & 3.73 & AREAL \\
3 & 14469 & 0 & 6.48 & 55 & -14.9 & -6.9 & 54.1 & -23.1 & 0.374 & AREAL \\
2 & 1971 & 2.37E-16 & 5.26 & -51.1 & 25.6 & -10.5 & -53.6 & 17.8 & 10.2 & AREAL \\
1 & 217 & 0.00214 & 4.55 & -4.48 & -13.7 & 10.3 & -6.46 & -14.9 & 9.96 & AREAL \\
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[t]
\caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for the contrast proper nouns (``ne'') > coordinate conjunctions (``kon'').}
\label{tab:cope3}
\begin{tabular}{rrrrrrrrrrp{3cm}}
\toprule
& & & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{5-7} \cmidrule{8-10}
Cl.\-Index & Voxels & $p_{corr.}$ & Z\-max & X & Y & Z  & X & Y & Z & structure \\
\midrule
9 & 7691 & 2.80E-45 & 6.23 & -61.2 & -22.3 & 11.6 & -55.9 & -20.7 & 4.03 & AREAL \\
8 & 5928 & 5.97E-38 & 5.5 & 57.5 & -26.2 & 15.9 & 58.2 & -15.8 & 3.55 & AREAL \\
7 & 479 & 1.13E-06 & 4.62 & -5.42 & -32.3 & 25.3 & -4.28 & -39.4 & 22.8 & AREAL \\
6 & 420 & 4.65E-06 & 4.85 & -4.76 & -71.4 & 40.1 & -3.74 & -68.5 & 36.2 & AREAL \\
5 & 407 & 6.38E-06 & 5.07 & 6.83 & -40.1 & 24.5 & 6.67 & -38.7 & 23.1 & AREAL \\
4 & 294 & 0.000115 & 4.57 & 17 & -69.1 & 34.6 & 17.7 & -67.1 & 34.9 & AREAL \\
3 & 121 & 0.0237 & 3.95 & 8.12 & -98.2 & 0.359 & 8.75 & -97.7 & -3.15 & AREAL \\
2 & 117 & 0.0274 & 4.38 & 36.9 & -24.8 & 4.55 & 37.4 & -23 & 3.09 & AREAL \\
1 & 115 & 0.0295 & 4.08 & -44.6 & -71.7 & 21.7 & -43.6 & -70.8 & 23.4 & AREAL \\
\bottomrule
\end{tabular}

@@

% descriptive Nouns
% hier ggf. noch angeben, dass die effektiv identisch waren
% Florian hat zwei Regeln falsch verstanden, sonst war übereinstimmung >90%
A further annotation of the audio-description's narrator was done manually: Two
persons performed a categorization of nouns embedded in sentences spoken by the
narrator to describe the movie's missing visual content. Categories focus on the
cinematographic scene's environment, inherent objects, persons, and a person's
appearance. A preliminary annotation according to the rules (s. ist jetzt in der obigen Tabelle aus Platzgründen nicht mehr drin; in dieser,\ref{tab:descr-nouns}, einer neuen Tabelle oder im laufenden Text [wird viel Text] bringen) was done by one person and corrected in several runs by the author.

@@

@@

@@

\clearpage
% der alte Entwurf der Tabelle; hier mit rules/description in der Tabelle
\begin{center}
\begin{tabular}{ |c|c|c|c| }
\hline
category & description & examples & count\\
\hline
geo & immobile landmarks & building, tree, street, alley, meadow, cornfield, river & 125\\
geo-room & rooms / locales; elements defining a locale's spatial layout & living room; wall, door, window, floor, turf & 105\\
setting\_new & first-time mentioned setting & on a bridge, on an alley, on campus & 86\\
setting\_rec & recurring setting & at the bus stop & 37\\
body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress, shirt & 66\\
bodypart & limbs and trousers & arm, finger, leg, toe & 69\\
face & face or parts of it & face, ear, nose, mouth & 47\\
head & non-face parts of the head; worn headgear & head, hair, ear, neck, helmet & 36\\
furniture & movable objects insides/outsides & bench, bed, table, chair & 50\\
object & countable entities with firm boundaries & feather, telephone, car & 232\\
objects & countable entities with firm boundaries & wheels, photos & 52\\
female & female person & nurse, mother, women & 31\\
females & female persons & women & 3\\
fname & female name & Jenny, Carla & 74\\
male & male person & man, father, soldier & 89\\
males & concrete male persons & boys, opponents & 23\\
mname & male name of person present in the scene & Forrest, Bubba, Kennedy & 291\\
persons & concrete persons of unknown sex / gender & hippies, patients & 17\\
++ & nouns, adverbial adjectives, and adverbs & in the evening, it's daytime, later \\
\hline
\label{tab:descr-nouns-old}
\end{tabular}
\end{center}

>>>>

\listoftodos

@@

% descriptive Nouns
% hier ggf. noch angeben, dass die effektiv identisch waren
% Florian hat zwei Regeln falsch verstanden, sonst war übereinstimmung >90%
A further annotation of the audio-description's narrator was done manually: Two
persons performed a categorization of nouns embedded in sentences spoken by the
narrator to describe the movie's missing visual content. Categories focus on the
cinematographic scene's environment, inherent objects, persons, and a person's
appearance. A preliminary annotation according to the rules (s. ist jetzt in der obigen Tabelle aus Platzgründen nicht mehr drin; in dieser,\ref{tab:descr-nouns}, einer neuen Tabelle oder im laufenden Text [wird viel Text] bringen) was done by one person and corrected in several runs by the author.\todo{I thought we said that this aspect should move to the PPA paper?}

@@

\todo[inline]{If the descriptive nounes are moved to the PPA paper, this table should be removed}

@@

\begin{figure*}
  \centering
% \includegraphics[width=0.4\textwidth]{frog.jpg}
  \includegraphics[width=\linewidth]{figures/slicescolorbars}
  \caption{Mixed-effects group-level (N=14) GLM contrasts for the audio-description of the movie Forrest Gump. All cluster (Z>3.4, p<0.05; cluster corr.; MNI template space).}
  \label{fig:results}
  \todo[inline]{Figure not referenced in the text}
\end{figure*}

\begin{table*}[t]
    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for the contrast words > no-speech.}
\label{tab:cope1}
\begin{tabular}{rrrrrrrrrrp{3cm}}
\toprule
& & & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{5-7} \cmidrule{8-10}
Cl.\-Index & Voxels & $p_{corr.}$ & Z\-max & X & Y & Z  & X & Y & Z & structure \\
\midrule
4 & 14990 & 0 & 6.31 & -49 & -24.7 & 6.35 & -54.8 & -32.5 & 3.73 & AREAL \\
3 & 14469 & 0 & 6.48 & 55 & -14.9 & -6.9 & 54.1 & -23.1 & 0.374 & AREAL \\
2 & 1971 & 2.37E-16 & 5.26 & -51.1 & 25.6 & -10.5 & -53.6 & 17.8 & 10.2 & AREAL \\
1 & 217 & 0.00214 & 4.55 & -4.48 & -13.7 & 10.3 & -6.46 & -14.9 & 9.96 & AREAL \\
\bottomrule
\end{tabular}
  \todo[inline]{Table not referenced in the text}
\end{table*}

\begin{table*}[t]
\caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for the contrast proper nouns (``ne'') > coordinate conjunctions (``kon'').}
\label{tab:cope3}
\begin{tabular}{rrrrrrrrrrp{3cm}}
\toprule
& & & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{5-7} \cmidrule{8-10}
Cl.\-Index & Voxels & $p_{corr.}$ & Z\-max & X & Y & Z  & X & Y & Z & structure \\
\midrule
9 & 7691 & 2.80E-45 & 6.23 & -61.2 & -22.3 & 11.6 & -55.9 & -20.7 & 4.03 & AREAL \\
8 & 5928 & 5.97E-38 & 5.5 & 57.5 & -26.2 & 15.9 & 58.2 & -15.8 & 3.55 & AREAL \\
7 & 479 & 1.13E-06 & 4.62 & -5.42 & -32.3 & 25.3 & -4.28 & -39.4 & 22.8 & AREAL \\
6 & 420 & 4.65E-06 & 4.85 & -4.76 & -71.4 & 40.1 & -3.74 & -68.5 & 36.2 & AREAL \\
5 & 407 & 6.38E-06 & 5.07 & 6.83 & -40.1 & 24.5 & 6.67 & -38.7 & 23.1 & AREAL \\
4 & 294 & 0.000115 & 4.57 & 17 & -69.1 & 34.6 & 17.7 & -67.1 & 34.9 & AREAL \\
3 & 121 & 0.0237 & 3.95 & 8.12 & -98.2 & 0.359 & 8.75 & -97.7 & -3.15 & AREAL \\
2 & 117 & 0.0274 & 4.38 & 36.9 & -24.8 & 4.55 & 37.4 & -23 & 3.09 & AREAL \\
1 & 115 & 0.0295 & 4.08 & -44.6 & -71.7 & 21.7 & -43.6 & -70.8 & 23.4 & AREAL \\
\bottomrule
\end{tabular}
\todo[inline]{Table not referenced in the text}

@@

\clearpage
% der alte Entwurf der Tabelle; hier mit rules/description in der Tabelle
\begin{center}
\begin{tabular}{ |c|c|c|c| }
\hline
category & description & examples & count\\
\hline
geo & immobile landmarks & building, tree, street, alley, meadow, cornfield, river & 125\\
geo-room & rooms / locales; elements defining a locale's spatial layout & living room; wall, door, window, floor, turf & 105\\
setting\_new & first-time mentioned setting & on a bridge, on an alley, on campus & 86\\
setting\_rec & recurring setting & at the bus stop & 37\\
body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress, shirt & 66\\
bodypart & limbs and trousers & arm, finger, leg, toe & 69\\
face & face or parts of it & face, ear, nose, mouth & 47\\
head & non-face parts of the head; worn headgear & head, hair, ear, neck, helmet & 36\\
furniture & movable objects insides/outsides & bench, bed, table, chair & 50\\
object & countable entities with firm boundaries & feather, telephone, car & 232\\
objects & countable entities with firm boundaries & wheels, photos & 52\\
female & female person & nurse, mother, women & 31\\
females & female persons & women & 3\\
fname & female name & Jenny, Carla & 74\\
male & male person & man, father, soldier & 89\\
males & concrete male persons & boys, opponents & 23\\
mname & male name of person present in the scene & Forrest, Bubba, Kennedy & 291\\
persons & concrete persons of unknown sex / gender & hippies, patients & 17\\
++ & nouns, adverbial adjectives, and adverbs & in the evening, it's daytime, later \\
\hline
\label{tab:descr-nouns-old}
\end{tabular}
\todo[inline]{If the descriptive nounes are moved to the PPA paper, this table should be removed}
\end{center}
